\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-05-07 doc/incertae_sedis.tex
minor changes to avoid name repetition across figures 1 and 2

However, in the \emph{incertae sedis} framework, it is possible for one name to
apply to multiple nodes. For example, in Figure \ref{fig:One-name-can}b, the
name $A$ can apply to nodes $x$ and $y$. Here the name $A$ corresponds to the split
$A1\,A2\,|\bullet B\,C$, leaving out $D$ since it is \emph{incertae sedis}. The two nodes $x$
and $y$ display the splits $A1\,A2\,|\bullet B\,C\,D$ and $A1\,A2\,D|\bullet
B\,C$ respectively, and both
of these splits display the split $A1\,A2\,|\bullet B\,C$, so the name $A$ can apply to both
$x$ and $y$. This cannot happen without\emph{ incertae sedis} taxa except at
monotypic nodes. When faced with a choice about where to place a name, our
solution is to find the most tip-ward node where the name can apply and attach
the name to this node. This corresponds to a conservative choice about whether
\emph{incertae sedis} taxa should be added to an existing taxon.

>>>>

However, in the \emph{incertae sedis} framework, it is possible for one name to
apply to multiple nodes. For example, in Figure \ref{fig:One-name-can}b, the
name $E$ can apply to nodes $x$ and $y$. Here the name $E$ corresponds to the split
$E1\,E2\,|\bullet F\,G$, leaving $H$ out of the definition since $H$ is \emph{incertae sedis}. 
The two nodes $x$
and $y$ display the splits $E1\,E2\,|\bullet F\,G\,H$ and $E1\,E2\,H|\bullet
F\,G$ respectively, and both
of these splits display the split $E1\,E2\,|\bullet F\,G$, so the name $E$ can apply to both
$x$ and $y$. 
This cannot happen when the rooted splits that correspond to a taxonomic name
    are generated without\emph{ incertae sedis} taxa except at
monotypic nodes.

This situation is the result of the fact that it is not clear whether the names
    in the taxonomic tree should be treated as node-based or branch-based
    phylogenetic defintions.
A node-based definition of $E$ would be ``the clade rooted at the MRCA of $E1$ and $E2$ as long as it is not
    the ancestor of $F$ or $G$''; this would correspond to node $y$ in the solution
    depicted in figure Figure \ref{fig:One-name-can}b.
The branch-based definition would take the form ``The clade containing all lineages more closely related to 
   $E1$ and $E2$ than to either $F$ or $G$, if such a clade exists''; this definition
   would include node $x$ and the lineage connecting it to its parent.
The ambiguity arises because both definitions refer to the same node in the taxonomy,
    so it is unclear which is a preferable way to define the taxon concept of $E$.

When faced with a choice about where to place a name, our
solution is to find the most tip-ward node where the name can apply and attach
the name to this node.
This corresponds to using a node-based definition of the taxonomic names.
The result of this naming choice is that the algorithm is conservative with respect
    to when the \emph{incertae sedis} taxa should be placed within another named
    taxon.

Note that the intrusion of an \emph{incertae sedis} taxon within another taxon does not
    always lead to ambiguity in which node should be named. 
For example, $H$ is placed inside taxon $EF$ in Figure \ref{fig:One-name-can}, but the
    the name $EF$ only applies to one node in the solution tree.
